\textbf{Oct 19 2018}\\
  \textbf{Progress:}
  We meet as a group and completed our problem statement, as well as decided how to do the next assignment. We also met our ta.

  \textbf{Problems:}
  Team Member still want access to VR headsets, as per client request. We are still figuring that out. The client in out of the country for the next week.

  \textbf{Plans:} 
  Figure out the VR gear situation and work together too complete the requirements document.\\

\textbf{Oct 26 2018}\\
\textbf{Progress:}
We have each been completing sections of the requirement document, with updates nearly every day. We each divided the outline of the document as fair as possible. Along with team members are starting to look into downloading the Unreal Engine and start learning. We have also discussed possible tech resource topics, that would be interesting based on each owns interests in the project. For example, I will probably be looking into which tools to use for recording, editing, and layering sound files.

\textbf{Problems:}
We won't have time to let the client review the draft, due to him being on vacation, but this can be done later. The extended due date also helped with other class requirements and our own planning.

\textbf{Plans:}
Have the documentation ready to go before submission date. I will also start training on Unreal, as well as refreshing myself on other tools I will know I need, such as Maya, Reaper(Sound Studio), and Photoshop.\\

\textbf{Nov 2 2018}\\
\textbf{Progress:}
On Friday we met out client, Tim, and got a tour of HP's printer press and he shared some ideas of what he would like to see. We got good notes and a better idea of our scope. However, Tim does favor a large goal, so we have to stay on top of him when he gets excited and talks about what he wants to see in a couple years.

\textbf{Problems:}
Tim still wants us to be able to have headsets at home to play with. He understand that McGrath wants us to wait, so he will try and ask around HP in attempt to get us a couple now. He doesn't necessarily want us to start, but learn the interface of existing games and feel and respond in VR. This is due to the nature of many team members never trying VR.

\textbf{Plans:}
Tim wants to start meeting weekly now that he is back from Israel. He also invited us to work at HP once a week for about 2 hours if we wanted too. Looking forward, we will start to focus on more formal goals when talking to Tim, which will lead to hopefully the planning and design of our first scenario.\\

\textbf{Nov 9 2018}\\
\textbf{Progress:}
We finished up our tech reviews and looked over each others, as well as doing peer review with other teams. I have started training on Unreal, and we emailed the client on if he had updates for us concerning test files, NDA, and getting a training manual.

\textbf{Problems:}
We still are waiting on the training manual so we can finalize a strong plan on specifically what training scenario we will plan for. Hopefully the client will give us this next week, our design document will need to rely on it.

\textbf{Plans:} 
keep in touch with the client and plan to meet hopefully sometime next week at HP. We all also agreed to start actually learning unreal instead of just thinking about it, hopefully we all have time for this.\\

\textbf{Nov 16 2018}\\
\textbf{Progress:}
This week we talking about starting the design document and what we need to do with the one we already started to ensure it meets the requirements.

\textbf{Problems:}
We have been emailing Tim our client however we have yet to receive a response in two weeks, hopefully next week....

\textbf{Plans:}
Keep emailing Tim every 2 business days so we can get things moving forward. Start working on the design document.\\

\textbf{Nov 23 2018}\\
\textbf{Progress:}
Working on the design document, got email back from client requesting a NDA, hopefully meet with him next week. It was a short week due to holidays so progress is limited.

\textbf{Plans:} 
Sign the DNA and meet client so we can get access to company CAD models to start project. Finish Design Document by due date.

\textbf{Problems:} 
Weekend plans with the holidays made it so we couldn't meet client this week, but overall it is not that important.\\

\textbf{Jan 11 2019}\\
\textbf{Progress:}
emailed Mcgrath for hardwarew and he ordered some hp headets. Emailed Tim to let him know when we are available to meet at HP. Everyone is now getting together and learning unreal.

\textbf{Problems:}
Waiting on CAD files and documents from HP.

\textbf{Plans:} 
Hopefully get CAD files and training docs to flesh out a more detailed task list of goals.\\

\textbf{Jan 18 2019}\\
\textbf{Progress:} 
Found out where to get most of our art assets for free, so we will not have to make a lot of generic office furniture and supplies to create our 3d world. Everyone is still working on unreal and getting stuff put together. We also now have enough headsets for everyone in the group which is awesome.

\textbf{Problems:}
no word from client. This isn't holding back on the short term as we learn tools and get things together, but will hurt long term goals if he doesn't reach out soon.

\textbf{Plans:}
keep trying to get in touch with out client. Keep playing in unreal and starting building our test environment. Setup up git with Unreal, start creating agile tasks and weekly outlines.\\

\textbf{Jan 25 2019}\\
\textbf{Progress:} 
Finally met with client, got more detials and quest requirements. Got some CAD files to work with. Found out how to get all the other models we should need. Level design is coming along. Unreal is becoming more familiar.

\textbf{Problems:} 
Still need to get repo running, should have that done soon.

\textbf{Plans:} 
Get Unreal repo, make sure everyone is on the same page, and start getting user stories done.\\

\textbf{Feb 1 2019}\\

\textbf{Progress:}
Completed rough draft 3d printer models. Me and Nick also met Tim at HP on Wednesday to take photos and gather more information. We also met team as a group on Friday and discussed team progress and goals before the next meeting.

\textbf{Problems:}
Cad files to large for my system memory to import, causing crashing after about 45minutes of attempting to upload. Ending up wasting a lot of time with this. Instead, I am freestyling the models based on images rather than cad models.

\textbf{Plans:}
Finish the models and animations this weekend so we can start too implement printer features in VR.\\

\textbf{Feb 8 2019}\\
\textbf{Progress:}
Models are done and in the game engine, we have built a factory environment, also created and added models that are found at HP. 

\textbf{Problems:} 
some of the models doors have pivoting issues, will need to edit this. UV mappings in some Sketch-up models are also causing texture issues. 

\textbf{Plans:} 
I plan on fixing the 3d pivot issues this week, and redo the imported Sketch-up models UV wrappings too allow proper texturing. Start the tutorial features with group and specific in game printer features, like inserting new printer heads in the printer.\\

\textbf{Feb 16 2019}\\

\textbf{Progress:}
Fixed all model issues, met with Tim and review the level of detail of models and his thoughts on what we have.

\textbf{Problems:} 
No real problems at the moment just good overall team progress.

\textbf{Plans:} 
Meeting on Sunday too work on alpha stage requirements. Should be getting a good sprint in to show off new features to Tim next week.\\

\textbf{Feb 23 2019}\\
\textbf{Progress:}
Figuring out how to integrate Stewards UI into printer scenarios.

\textbf{Problems:} 
Been out with the flu since Wednesday and still recovering, hadn't been able to work as much as I would like.

\textbf{Plans:}
Finish printer scenario by next week with team.\\

\textbf{Mar 1 2019}\\
\textbf{Progress:} 
Debugged blueprints to fix problems concerning printer interaction. Taking printer pieces out had three bugs and they are now taken care of.

\textbf{Problems:} 
No real issues. Client was sick so no weekly meeting, and possible issue with McGrath strongly recommending not to do a live demo during expo.

\textbf{Plans:}
Get doors functions in a way that feels good in VR. The doors are function kinda like trunks of cars and open upward by rotation. It might get tricky figuring out how too rotate it according too user hands.\\

\textbf{Mar 8 2019}\\
\textbf{Progress:} 
Me and Symon got together and recorded all the voiceover and sound effects we need. I also edited and compiled all sounds into files for unreal

\textbf{Problems:}
Nothing to much, the client is still sick and is then going on a vacation next week, so we wont see him for a while.

\textbf{Plans:} 
Finish blueprints for player experience. \\

\textbf{Mar 15 2019}\\
\textbf{Progress:}
finished blueprints for printer doors. They don't quite have the animation I wanted, but they are at least functional.

\textbf{Problems:} 
No Tim for the rest of the term, but we do have good progress and he know we are on track.

\textbf{Plans:} 
Meeting on Monday to record video and finalize documentation for the term.\\

\textbf{Apr 5 2019}\\
\textbf{Progress:} 
We meet as a group multiple times and discussed our plans and goals going forward into code freeze.

\textbf{Plans:} 
Hopefully meet with Tim next week and decide on last minute additions and approve our revised documents. I will also be adding better animations too doors, and fixing various UV wrapping issues with some of the Datasmith Models.

\textbf{Problems:} 
No problems this week, we are all ready to move forward to finalize the application.\\

\textbf{APR 12 2019}\\
\textbf{Progress:} 
met as a group and decided what needed finished up on remaining documents. We also got done everything for code freeze.

\textbf{Plans:} 
I will check over project one more time, to if there is anything I can improve this weekend.

\textbf{Problems:} 
Still no contact from client.\\

\textbf{APR 19 2019}\\
Code freeze went well and we all worked together to making sure it was ready.
We finally heard back from Tim but he wont be able to meet with us yet to submit design doc.\\

\textbf{Apr 27 2019}\\
We got a hold of our client this week. We met up and finalized poster over slack. Nothing else really going on at the moment.\\

\textbf{May 3 2019}\\
Havnt done too much this week, we did wrap the poster. Otherwise we are all ready to go for expo.\\

\textbf{May 10 2019}\\
Nothing really to report this week. We haven't able to reach our client in some time. Like 4 weeks. Hopefully that is nothing to worry about. Otherwise we should be good for expo.\\
