\subsubsection{Fall}

\textbf{Oct 12, 2018}\\
1. Progress: I reached out to my contact at HP, Tim Holt, to convey my interest in the project. I listed my experience with Virtual Reality and asked him questions about the project as well. After I was selected for the project, I came into contact with my team and met with them prior to class. We discussed initial steps and figured out our next course of action.
\\
2. Problems: No significant problems this week. I had to decide the order of projects I wanted to do. 
\\
3. Plans: Work on the individual Problem Statement assignment. Contact Tim Holt as a group to notify him of our group and to set-up an initial meeting.
\\
\textbf{Oct 19, 2018}\\


Progress: 	Our team met together and we have been able to develop more rapport. I'm really enjoying working with them. They seem very competent and easy-going, which makes me feel like I'm going to enjoy this project. The slack is very active as well. We met with our client, Tim Holt, at Block 15 and discussed the project into further detail. He brought the mixed-reality headset that we are going to be developing on and we were able to go through a quick demo. The Problem Statement was also finished and I enjoyed working on that.  \\
Problems: 	The only contingency we encountered was that Tim Holt will be going on vacation all of next week, so we will not be able to be in contact with him for a brief period of time. It's not a large concern, however, as our meeting with him was very productive and we were able to gather more knowledge about what we are going to be doing as well as background information on VR/HP/our client. \\
Plans: 	The group problem statement and the Client Requirements Document are what is on the agenda and will be the focal point of what we will be working on going forward. The Problem Statement should be more or less a mesh of all the individual assignments we have. The Requirements Document will first require us to divide up the work between the five of us.\\
\textbf{Oct 26, 2018}\\
Progress: 	This week, we were tasked to write our Group Problem Statement and first draft of our Requirements Document. We were able to finish our group problem statement in a single sitting and we are making great progress on on our Requirements Document. I found that everyone on our team is enthusiastic about this project, which really helps make the experience so much better. Enthusiasm is a great motivator in team centered projects like this one. \\
Problems: 	We have not run into any major problems yet. Our client is currently away on vacation for this week, so we aren't able to meet with him to discuss the Requirements Document, but we have enough information from our previous meeting and his project post to flesh out our document to the extent we want to. We were also not able to coordinate a time where all 5 of us could go to HP and take a look at the printers.\\
Plans: 	The plan going forward is to finish the Requirements Document on time and flesh it out so that it's presentable to Tim for the next time we meet with him. We will plan to meet and work on it together. Because we are using overleaf to develop the document, we can all work on it on different computers and at different times. We've already assigned the sections we'll work on, which will help our organization going forward.\\
\textbf{Nov 2, 2018}\\

Progress: 	
This week, we've been tasked with turning in the Client Requirements Document, the Tech Review, and Team Standards. The Requirements document has been turned in and submitted as well as the team standards document. The Tech Review, while an individual assignment, required us to delegate by concepts so as to not run into overlaps when we join all of our tech reviews into a single document. I am making great progress on the Tech Review and selected the task of comparing Virtual Reality, Augmented Reality, and Mixed Reality. In terms of the overall progress on the project itself, we have made some contact with our client, who has been away for a week on vacation, which is good. He is currently going over the requirements document.\\

Problems: 	The initial requirements document that we created, while was lengthy and well-made, ultimately did not fit the criteria of what a requirements document should look like, and was better categorized as a design document. Requirements documents should be more high level and focus on the basic aspects of the project, such as what problem we are trying to remedy. While this wasn't a significant hiccup, it did require us to re-write our requirements document. Still, we can use what we wrote as part of our design document in the future.\\
Plans: 	The plan going forward is to continue working on the documentation assignments assigned for us and begin pursuing our client to meet more and gain more information related to our project. One objective we have by the end of the term is to acquire and analyze the training manuals that HP has regarding the printers we are creating training modules for.\\
\textbf{Nov 9, 2018}\\
Progress: 	The progress for this week has been great. We met with our client at HP to tour the WebPress printers. I took 6-7 pages of notes and compiled them for my team to view and for our reference. We have a good direction of where we want to go in terms of the project as a whole. In the day-to-day, we've mostly had writing to do. We have been working on the Tech Review documentation. My tech review analyzed the applicability of Virtual, Augmented, and Mixed Reality, which I found very fun to write. It also helped me think more about why we are using Virtual Reality for this project and what alternatives we have/why we aren't going a different route. In addition, our client said that he will appeal to his bosses to see if we can acquire some headsets for our development use, which would be great going forward. \\
Problems: 	No problems occurred for this week. Last week, our initial requirements document turned out to be more of a design document. As a result, we had to re-write our requirements document, but fortunately, we now have a design document to use for future assignments.\\
Plans: 	We are currently awaiting our client to send us instruction manual documentation and a potential NDA agreement for the CAD models that we are going to be referencing. We are also in the process of completing what assignments are given to us. \\

\textbf{Nov 16, 2018}\\

Progress: 	No major writing assignments were due this week. We sent out an email to our client prompting him for the instruction manuals and other materials that could be helpful for us in the meantime. There was no class on Tuesday because of the MECOP Fall Event. \\
Problems: 	Our client hasn't responded to our email in a while. We will be sending a follow-up email soon in an effort to be pro-active about our project. Other than that, no significant problems have occurred. One small thing to note would be our Requirements Document not being in correct IEEE format - we will need to make adjustments for future documents.\\
Plans: 	We have the Design Document assignment due in two weeks. I think that it will go well because we had accidentally written most of it for what we thought would be our requirements document. There are still some modifications that we will need to make, such as the addition of user stories and other specific details that the Design Document needs, but expanding on the info won't be very laborious. Overall, things are projected to go well.\\

\textbf{Nov 23, 2018}

Progress: 	This was a shortened 3-day week because of Thanksgiving. In those three days, no significant assignments were due. We have the design document due early next week that we will want to complete. Our client also sent us an NDA for the CAD models that we are going to be using. \\
Problems: 	My team and I were hoping to work on the design document a little bit prior to the break, but we ended up not being able to coordinate a time for all of us to meet up. Still, we have a lot of the design document completed because of how our requirements document was initially structured.\\
Plans: 	Plans going forward include working on the design document together and signing the NDA for the CAD models. We expect to get together either next Monday or Tuesday. \\

\subsubsection{Winter}

\textbf{Jan 11, 2019}\\
Progress: 	While we didn't end up having a Thursday class and the Tuesday class was a short introduction to the Winter Term portion of Capstone, our team has been able to coordinate our TA meeting and reach out to our sponsor and instructors about regular meeting times for this term and the acquisition of HP headsets for development purposes. While no implementation and programming was done as we were getting into the swing of things, we certainly have a direction going forward. \\
Problems: 	No significant problems occurred. There was a slight bit of confusion with our group and the instructor in our email correspondence to acquire HP headsets, but we were able to get everything sorted.\\
Plans: 	In the immediate future, we are hoping to acquire two HP headsets courtesy of the Capstone instructors. With this, along with a concrete time availability with which we can meet with our client and develop our program, we can have a foundation for our work going forward. \\
\textbf{Jan 18, 2019}\\

Progress: 	McGrath was able to get us three Windows Mixed Reality headsets, which was more than we had asked for! With this, we would be able to develop at a faster rate. We are getting acquainted to Unreal and dipping our feet into the development cycle as well. In regards to class, we didn't have any, but we were able to meet briefly and communicate through Slack.\\
Problems: 	Although we sent out an email to our client about setting up a meeting, he hasn't responded yet. We plan to send a follow-up email soon in order to make sure everything gets set-up. At HP, we would have access to some top-line computers that could aid in our development of the training modules. Another problem worth noting is that although we are hoping to have our meeting and development time be on Monday, we might not be able to meet next week because of the holiday.\\
Plans: 	Plans going forward include sending the follow-up email to our client and beginning development of our training module. One aspect for us to consider would be to look into the documentation and review possible training scenarios that could benefit us.\\
\textbf{Jan 25, 2019}
Progress: 	We were able to meet with Tim Holt, our client, earlier today! We discussed our direction going forward and he gave us CAD models which we can use as reference. We have an idea of what kind of training module we want to build as well as certain details we'd like to consider, such as how much hand-holding we should provide for the user. We scheduled meeting times and were able to dip our feet into Unreal more and more. Most of the team was able to use the VR headsets that we acquired from the instructor with success as well.\\
Problems: 	No significant problems occurred. This was mostly another set-up week and it looks like we'll be able to start actual development in a team setting next week. \\
Plans: 	In the immediate future, I'm tasked with summarizing the notes in an email and sending it out to the team and Tim. Fortunately, we were able to schedule a regular meeting time with Tim at 12 PM on Fridays. We also set aside a development time for Monday afternoons where the entire team can work together, most likely in the Bachelor Hall VR Lab because all the computers have Unreal installed. \\

\textbf{Feb 1, 2019}
Progress: 	Our team is now getting started on actual project development. I've parsed through the Operator Manual for the Web Press systems and took extensive notes on possible scenarios and intricacies that we might want to account for. I've also looked into SUS forms for when we receive feedback on our system. Our team has also set-up Github with our project and have begun working on the scenario and playing around with it using the VR headsets. Our level prototype is going to comprise of accurate room geometry, a basic model of the Web press, and other smaller models, such as desks, chairs, and computers.\\
Problems: 	I regrettably missed the TA meeting with Chris this week, which isn't something that should become a habit. I've added multiple alerts on my calendar to ensure it doesn't happen again as it's a really important meeting to have to make sure we're all on the same page.\\
Plans: 	Going forward, we hope to be able to implement a basic environment with a Web Press model that allows the user to interact with it in a simple way. We'll be meeting with Tim later this Friday to showcase it. Along with that, we are going to continue developing the models for all of the different parts of the Web Press that we are going to implement. We will also be going to HP to take pictures and notes of the Web Press to use as reference.
\\
\textbf{Feb 8, 2019}\\
Progress: 	Stephen has been able to develop prototype models of the Web Press printer, the Unwinder, and Rewinder and Stewart is working on the UI for our modules. Kyle, Nick, and I have been working on creating the environment and filling it with models of items, such as chairs, cabinets, safety tape, and so forth. I've also been going through the documentation of the Web Press and have parsed through ~300 pages of documents so far and found some plausible ideas as to how we should model our training scenarios and environment. We also met with another team to go over our Poster and found many areas of improvement that we can do.\\
Problems: 	No significant problems occurred this week. The only small one I can think of is that because of the snow day, we were unable to meet with our TA. \\
Plans: 	We're getting further along with development and the entire team is cohesive and wanting to get work done and meet frequently. Tomorrow, we have our meeting with our client to go over the latest rendition of our prototype. We'll be bringing the headset in for him to explore the environment. \\
\textbf{Feb 15, 2019}\\

Progress: 	We have been able to implement the entire Web Press environment with a model of the printer, various models that help construct the environment we are trying to replicate, and base functionality of moving certain objects. I created an infographic of instructions on how to use the controllers.  \\
Problems: 	No significant problems have occurred this week. Last week, we were unable to meet with our client and we sent him a follow-up email to see if we can get a meeting scheduled this week.\\
Plans: 	We are planning on working on implementing a training module in our next step to add actual functionality for the environment. I've been parsing through the training manuals looking for possible scenarios to use. We are also going to meet with our client on Friday (hopefully) to go over what we have so far. We are going to get started on the rough draft of the Winter Term reporting as well.\\
\textbf{Feb 22, 2019}\\
Progress: 	After setting up the environment, we've now completed the first part of the tutorial (looking at specific points). In regards to the printhead replacement, we've been able to implement blueprints for picking up printheads and putting them back into the printer. We've also updated our printhead replacement workflow to include references to the HP Web Press manual. We also updated our Expo Poster with the suggested sessions from our critique session. We also wrote up our Winter Term progress report. \\
Problems: 	No significant problems occurred this week. We weren't able to get as much done as last week because of other work and classes, but we've been able to work here and there. \\
Plans: 	Going forward, we should implement the teleporting/picking something up parts of the tutorial as well as get started on the printhead replacement workflow. We should hopefully have a working alpha release by Monday. 
\\
\textbf{Mar 1, 2019}\\

Progress: 	Class-wise, we created our progress report and summarized our progress in addition to reviewing another group's. This week, I created a System Usability Scale form customized for our project in addition to a modified Printhead Replacement workflow that references certain sections of the Web Press documentation. In regards to the current state of the project, we are still undergoing development of the Printhead Replacement workflow. We've made some progress, but due to sickness, we've been unable to make as much progress as we would have hoped for this week. \\
Problems: 	We had some issues with the UI being rendered too small with an HP headset versus an Oculus, which was what was being used for development. We also had our client meeting canceled because our client had the flu, but this gives us more time to refine our system and fix any bugs that we have with the Printhead Replacement workflow. \\
Plans: 	Going forward, we plan to complete the Printhead Replacement workflow so that it can be presentable at the time of our client meeting next week. Having this goal will enable us to strive to finish the last significant portion of our project requirements. 
\\
\textbf{Mar 8, 2019}\\

Progress: 	Some environmental items have been polished and more progress has been done in regards to the printhead installation workflow, but we still have to connect the blueprints that we have completed into an entire cohesive entity that can be presentable to our client. We've had discussions about the System Usability Scale and presenting the project to Nick's team at HP as well. We also attended class this week and talked with Kirsten regarding the state of our project and how we can set up for the Expo. We decided for the Expo to have a live demo and hopefully a video to play in the background as well.\\
Problems: 	Unfortunately, our client was sick this last meeting and we haven't been able to meet with him regularly. We also haven't had many opportunities to code together in small groups, rather opting to work more individually on our parts and discuss via Slack because of our conflicting schedules and classes. However, we have been able to make some progress nevertheless.\\
Plans: 	Going forward, we plan to continue working on the replacing printhead workflow. Getting this done is the top priority. I've been tasked with creating atmospheric sounds and voice-over dialogue of our user interface scripts. I will be collaborating with Stephen in making these. It would be important for us to adhere to the workflow diagram created so that it will definitively match the UI. 
\\
\textbf{Mar 15, 2019}\\
Progress: 	We have completed 80-90\% of the base scenario. Once we complete that and incorporate the recordings that we made, all that would be left are finishing touches to our project, in addition to documentation and program verification. The blueprints of the last portions of the base scenario are also completed. By incorporating those into the printhead replacing workflow, we'll have a more cohesive narrative.\\
Problems: 	No significant problems have occurred. We were unable to meet with our client last week and we hope to set a meeting with him this week, but either way, we've been able to progress with our project with the initial direction that we were given.\\
Plans: 	Going forward, we are going to finish up the base scenario and present it to Nick's team (possibly next Tuesday). We will also ask them to fill out a System Usability Scale per our design document expectations. We'll also potentially present it to other notable individuals, such as Dr.Di Amici, who specializes in Virtual Reality. We will also complete the progress report in addition to the progress video to summarize our progress for this term. 
\\
\subsubsubsection{Spring}

\textbf{Apr 5, 2019}\\
Progress: We were able to meet together as a team and figure out a good time to meet regularly with both our TA and our client. We also attended class and were able to get more information on the term. Overall, this was mostly a set-up week to get us ready for the rest of the term. We also learned that we should create a user guide and an installation guide in our github repo. We spoke to Ben about having an executable file and he said that it's fine so long as our source code is easily found as well.
\\
Problems: No significant problems occurred this week.
\\
Plans: Going forward, we are going to focus on refining aspects of our project, making sure that all significant bugs are dealt with. That is our minimum goal: to make sure that our product is viable at minimum. One goal that we will have is to incorporate audio into the project. We already have the audio recorded, so all that will need to be done is to configure the audio to play based on which step the user is on.
\\

\textbf{Apr 12, 2019}\\
Progress: We are in the process of implementing the audio and fine tuning our environment for refining purposes. The other big aspect we will be tackling by the end of this week is the user guide and the installation guide. We also had our TA meeting on Thursday. We also verified that everything we have is working properly, looking into fixing bugs and spelling mistakes. 
\\
Problems: We have been unable to contact our client since late March, which is turning into a slight concern as we have been unable to meet with him yet this term. We will be contacting him again soon to prompt for another meeting so that we can get on the same page. 
\\
Plans: We will be working on the user guide and installation guide more, in addition to cleaning up the GitHub so that it can be presentable. Code Freeze is next monday, so the final refinements are also a very important item to tackle. 
\\

\textbf{Apr 19, 2019}\\
Progress:
\\ In terms of progress, we were able to prepare our repository and project for code freeze and finish up any document verification we had to do. Everything seems like it is smooth sailing.
\\
Problems: We have been having much difficulty contacting our client, and though he responded to us recently, we have worries that he will not be able to complete our document verification in a timely manner. We haven't been able to meet with him and he has been aloof for the past several weeks.
\\
Plans: Going forward, we are probably going to refine our project where we can and prepare it for Expo presentation. We are also going to need to attend one of the lectures offered over the course of the next few weeks.
\\
\textbf{Apr 26, 2019}\\
Progress: We submitted our project before code freeze and have taken our group photo. We also touched base with Chris about what we have to do going forward. There isn't much more to do other than Expo for Capstone.
\\
Problems: No problems occurred this week.
\\
Plans: The immediate thing we have to do is submit our project for Kirsten to review. Then, before May 1st, we will send the poster to be made for Expo. In addition, we also have actually attending the expo and preparing all of our content and supplies to get ready for it, but that shouldn't be too big of a trouble.
\\
\textbf{May 3, 2019}\\
Progress: We updated our poster for the expo and made sure that everything was submitted. Other than that, we haven't done much with the project. The last significant thing that we will need to do is show up to expo and make sure that our presentation is good. 
\\
Problems: No problems occurred this week.
\\
Plans: In terms of plans, we still have expo day circled on our calendar. We need to make sure that everything is set up for expo day and that we will be capable of providing a good experience to the people that we are presenting to. 
\\
\textbf{May 10, 2019}\\
No additional development on our project has been done. Class-wise, we attended today’s class and gained valuable knowledge for the Expo next week and in addition, we learned about future requirements post-Expo and how grades will be handled. Looking forward to the Expo!
\\