\textbf{Oct 19 2018}\\
  \textbf{Progress:}
Had our groups first meeting with the TA, although it was mostly introductions and describing our project.

Met with the whole group and worked together in person to finish the final draft of the problem statement. 

Had one member of the group inquire about getting more hardware (a VR headset) from the Instructor. 

  \textbf{Problems:}
Our client is out of the country for over a week, so will will either need to get an extension for the Requirements Document Rough Draft or just try and clarify any details with the client over the internet.  

While we are all supposed to try and familiarize ourselves with VR, only 2 members of the 5 member team already have a headset, and we haven't been able to get another yet. 

  \textbf{Plans:} 
Try and get another headset/organize possible group work times so that everyone can get experience with the headsets we have.

Work on the Requirements Document Rough Draft under the assumption that it has a hard deadline and try and maintain communication with the client over the internet. \\

\textbf{Oct 26 2018}\\
\textbf{Progress:}
Met with my group, mostly completed the requirements draft. 

\textbf{Problems:}
Our client has not gotten back from Israel yet, so we cant go over our draft of the requirements document with him yet.

\textbf{Plans:}
As the due date has been moved back tot he 30th, we will "finish" the draft and then schedule a meeting with our client to go over it with him. \\


\textbf{Nov 2 2018}\\
\textbf{Progress:}
Completed the individual tech review, completed the requirements doc even though we had to rewrite.


\textbf{Problems:}
Had to rewrite the requirements doc as we accidentally created the design document.


\textbf{Plans:}
Reestablish weekly communication with the client now that he is back from his international trip. Touch up the design document we made so that it can be ready to submit when that assignment is posted.\\


\textbf{Nov 9 2018}\\
\textbf{Progress:}
Uneventful week. We divided up the project so that nobody would have overlap for the Tech review and all submitted our individual assigned pieces. I was in charge of researching game/simulation perspectives and the different methods of user data collection. After some editing thanks to the peer review I was able to complete the final draft without issue.


\textbf{Problems:}
There were some initial difficulties dividing up the research as there are 5 members of the group (2 more than was expected in the provided example), and our project is relatively straight forward as far as our tech options go. In the end we were able to divide up the work so that nobodies tech review would be too barren.


\textbf{Plans:} 
As our design document is about 3/4 complete already, we plan to spend the week getting familiar with the development environment and the technology while meeting up with our client more to nail down any details we may have glossed over. We intend to meet before thanksgiving to finish that design document early as we should already know everything we need to complete it.\\

\textbf{Nov 16 2018}\\
\textbf{Progress:}
I worked on the Design Document a little, however progress has slowed on account of it being about 80\% complete and due over a week from now.


\textbf{Problems:}
Our group has not had contact with our client in a week. He haven't responded to our emails, although its probably just a case of our emails getting buried as he does get a lot of emails. 


\textbf{Plans:}
Our group plans to meet up soon, perhaps this following Monday, to finish the design document. We also sent out another email to get back in contact with our client so he can take a look at our draft. \\

\textbf{Nov 23 2018}\\
\textbf{Progress:}
Made contact with our Client again after a week of no contact. Got the confidentiality agreement document that we all must sign to get the CAD models.

\textbf{Problems:} 
With the holiday, most of the week vanished. Fortunately there were no pressing group activities to complete.

\textbf{Plans:} 
We are planing on signing the confidentiality agreement early next week. We also are going to meet up Monday or Tuesday to finish the Design Document Draft. \\


\textbf{Jan 11 2019}\\
\textbf{Report:}
Not much to report yet.

This week our group met back up, got in contact with our client (via email, still waiting for a new in person meeting) again after the break, requested hardware (x2 HP headsets instead of 1 Oculus to maximize portability) from Professor McGrath, and have a meeting for early next week planed so we can begin development.  \\

\textbf{Jan 18 2019}\\
\textbf{Report:} 
Our group met again early this week, unfortunately I was unable to attend the meeting and had to be briefed afterward. We were able to get 3 hp headsets and now we have VR development hardware for every member of the team. We will complete the poster and elevator talk assignments over the weekend and meet on Tuesday next week to begin dividing the work and starting full development. \\

\textbf{Jan 25 2019}\\
\textbf{Report:} 
Ya, this update is a little late. The end of the week was a bit busy. The group was able to meet up with our client on Friday for the first time this term. Were were able to get some CAD models to work off of and some more direction for our immediate project goals. Unfortunately due to schedules only 3 of us were able to attend the meeting directly, however we should be set. We have another group meeting Tuesday and we should have most tasks outlined and set to specific people (in Trello) then.\\

\textbf{Feb 1 2019}\\

\textbf{Report:}
This week we met with our client again (earlier today actually). We presented what we had worked on so far (a basic level, a model for the printer, re-worked VR movement, and a menu/ui widget that I made). Our client gave us positive feedback and helped direct us more toward a user experience that focused on people who might be totally new to VR. 

Looking forward we are going to continue to build the training room and printer, while also working toward a complete tutorial system. In the immediate, I plan on integrating my menu widget with the main branch over the weekend and then begin working on a dynamic checklist in the hud.\\

\textbf{Feb 8 2019}\\
\textbf{Report:}
While we weren't able to meet as a complete group this week outside of the meeting with the TA, we were all able to attend one of the meetups which were on Monday, Wednesday, and Friday (with our Client). I was able to attend the Wednesday work session/meeting and I was able to get the Menu and Interface code working with the main branch, although I am experiencing difficulties getting it onto the shared github. Next week I intend to complete the basic version of the Updating HUD/ Objective system so that we can begin implementing the tutorial and training scenario. \\

\textbf{Feb 17 2019}\\

\textbf{Report:}
This was an eventful week, I was able to get my working version of the menu program merged with the most recent version of the main project and get it on to the group repo. I was also able to get a working version of the dynamic HUD up and on the repo, so events should be easy to track.


We met with our client and once again he likes what we got and confirmed that we were on the right track.

My next goal is to complete the basic tutorial program so that new users can learn the basic controls and concepts of VR, and we will be meeting Sunday for group programming to that end. Most of the rest of the group will be working on the primary Training senario, and assuming the tutorial implementation goes well I will join them.\\

\textbf{Feb 23 2019}\\
\textbf{Report:}
This week I completed the tutorial section for the project. After a group meeting on Friday morning, we determined that a couple more sections may need to be added to the tutorial, however we should focus now on completing the main training scenario. We plan another group meeting/dev session on Sunday to focus on completing the main scenario. Things are moving along smoothly.\\

\textbf{Mar 1 2019}\\
\textbf{Report:} 
Fairly uneventful week, progress delayed on the main scenario due to most of our UE4 programmers (myself included) being sick over the weekend, which is my best availability for development. We were unable to meet with our client on Friday due to him  getting the flu. With everyone getting sick on top of the object interaction being far more buggy that we expected resulted in a very unproductive week. That should be fixed now that the object interaction has been fixed and people are no longer sick, and I plan to help get the scenario up and running over the weekend.  \\

\textbf{Mar 8 2019}\\
\textbf{Report:} 
This week was a really light week, we met early in the week as a group to assign the remaining tasks for beta release, but due to work loads most of us couldn't make begin making headway until Friday/the weekend. The goal is to have the senario mostly completed by Tuesday morning and then polished a bit by Friday to demo for our client. \\

\textbf{Mar 15 2019}\\
\textbf{Report:}
Over the weekend I was able to finish a rough but complete version of the primary scenario. With the rest of the team working on audio, blueprints for the printer panels, and level design polish. This next week I plan to finish up by adding a couple elements that I had to skip previously for time reasons, and then as a team we will incorporate the new assets and we should have the completed baseline before spring break begins. \\

\textbf{Apr 5 2019}\\
\textbf{Report:} 
 Met with the group, we didn’t do much over spring break (aside from Kyle working on a few features).We set out our plan for the project up to code freeze: Do a 2nd pass on the textures and models and improve what is unsatisfactory, fix strange control scheme bug, add sounds and the recorded voice overs into the project.Overall we are pretty much done.\\

\textbf{APR 12 2019}\\
\textbf{Report:} 
 Not much to report, project is nearly done. We met up and outlined the things that need to be done over the weekend: Finish user document for grading, get an executable version of the project tested. We’re still waiting to get contact with our client but there is no major thing we need to clear with him.\\

\textbf{APR 19 2019}\\
Not much to report, we were able to get the executable fixed so the project should run without issue for grading. We were able to make contact with our client again, however he only sent a short reply apologizing and saying that the delayed responses were due to him being very busy. We are still waiting for him to approve our documents, although nothing has changed in that area.\\

\textbf{Apr 27 2019}\\
Not much to report for this week, we got our documents confirmed by our client, took a group photo and finished our poster. We’re pretty much just waiting for expo.\\

\textbf{May 3 2019}\\
 Not much to report, everything, poster and all, is set and ready to go. next week we will walk through the set-up process so we have no issues at expo.\\

\textbf{May 10 2019}\\
 Last report, got all the info we needed this morning about expo and we should be all set. Nothing left to work on so im just looking forward to expo.\\
