\textbf{Oct 19, 2018}\\
This week was relatively slow in terms of progress on the project, but our group did move forward in the planning stage. We turned in our individual problem statements and then worked together to complete our group final problem statement. Everybody had a solid personal problem statement, so we really just took the best parts of each and combined them into a document we were all happy with. Another thing we did this week was get started on our requirements document. Lastly, we had our first meeting with our group TA.
One problem I foresee is that our client is going to be out of town for some of next week, and may not be available to go over our requirements document. Our group is also hoping to get access to VR headsets so that we can familiarize ourselves with the technology (per our client’s request), but are not sure how likely that is to happen soon.
Our plans include finishing up our requirements document, meeting with our client, and taking some time to learn Unreal Engine.\\

\textbf{Oct 26, 2018}\\
This week has been a little slow in terms of overall progress on the project. Our group is mostly dealing with creating a good requirements document that will serve as a good base from which to move forward on the project. I thought that the document would be a little simpler and less work than it is turning out to be. I'd say that is because this is the point where we are starting to dive deep into what is really going into this project, so there is a lot to flesh out. We plan on finishing the requirements document this weekend. After that I will be starting on the first draft of my tech review.\\

\textbf{Nov 2, 2018}\\
This week has been kind of a crazy one. Between midterms in other classes and fairly large writing assignments in this one, there hasn't been a whole lot of downtime. That being said, a lot of progress has been made this week. Our requirements document was turning out to be more of a design document than a requirements doc, so we had to start from scratch and create a more concise document. I made a tentative gantt chart to go along with that. We also worked on tech reviews, which turned out to be more fun and interesting than I had anticipated. I looked at virtual reality hardware, so ending up learning a lot about the differences between VR systems.
Our plans are to finish up the tech reviews, do peer reviews, and come together to create a final tech review.\\

\textbf{Nov 9, 2018}\\
This week was a relatively slow one, for this class at least. We did in class peer reviews on the tech reviews, which I found to be pretty helpful. I didn't end up having to change a whole lot of my paper, but getting more eyes on it helped, and it was interesting reading other people's work. Our group is starting to think about design document, which we kind of got  a head start on due to accidentally starting it instead of our requirements doc a couple weeks ago.
So the plan is to work on design and keep learning about tech in our spare time (VR, Unreal).\\

\textbf{Nov 16, 2018}\\
This was a pretty light week. There was nothing due this week, but we did start thinking about end-of-term stuff, like the design document and our progress presentation. So far there are no real worries, just have to continue knocking things off the list.
We contacted our client in the last week, to see if he wanted to meet again soon, and haven't heard anything back yet. I have also been meaning to work more with Unreal engine this term, but time hasn't really allowed, so hopefully I can brush up on it over Winter break!\\

\textbf{Nov 23, 2018}\\
This week we started looking forward to what all needs to be done before the end of this term. The group has met to talk about the design document and started working on it. It turns out that when we wrote our first draft of our requirements document it was basically a design document, so we have a good head start on this assignment. We will continue to work on that this weekend. Our client also got back to us about the NDA we need to sign in order to see HP's CAD models. It looks like we can all sign it and get the paper to him as soon as is convenient.\\

\textbf{Jan 11, 2019}\\
This first week the project did not move along all that much, mostly because we are all settling into new schedules and figuring out what our workflow is going to look like. The group is also getting more familiar with Unreal Engine, which is a project in and of itself. For my part I am learning more about the Unreal visual scripting system and level design tools. We also contacted Kevin about VR hardware and that should be arriving early next week. Lastly, we contacted our client in hopes of meeting up next week.
There were no real problems this week, but it is clear we need to get organized and start splitting up work.
Plans include meeting with our client next Monday, having our first TA meeting with Chris, getting version control setup for our project, and prototyping a rough level to test our newly acquired VR hardware.\\

\textbf{Jan 18, 2019}\\
This week we made a little bit of progress. We got hardware, more than we had thought we were going to get. Three HP headsets for me, Nick, and Symon to use because Stewart and Stephen have their own HMDs. Having those allowed us to play around with VR and get more comfortable with designing for the medium. I have also been using a lot more Unreal Engine, and am finally working my way up the steep learning curve associated with the tool. We also made a group Trello, so we can more easily track tasks, see what needs to be done, and who is doing it.
As for problems, there are a couple. We still haven’t heard back from our client at HP. We probably should have sent him a follow up email earlier in the week, but since it is Friday I think it is best if we wait to do it Tuesday morning (Monday is a holiday) to lower the chance the email gets lost in the abyss. I also am a little concerned with the amount of progress we have made on the project itself, which is little to none. We are all settling into the term, are busy, and learning new tech, but I think we need to make some serious headway in the next couple weeks and have a working prototype as soon as possible.
This next week the plan is to begin work in earnest on the project. We need to get a basic level up and running in Unreal and make sure we can use the VR headsets with our project. We also need to meet with our client and go over what the rest of development will look like. I think we will be okay, but we do need to start making some progress.\\

\textbf{Jan 25, 2019}\\
This week we made some good (mostly organizational) progress on the project. We set up more of the Trello board, which we are using to track tasks, got a shared Unreal project in Github, and met with our client to talk about the project. Our meeting with the client went really well, and he gave us some good ideas to bring into our work going forward. He gave us some CAD model files to look at, and suggested that we meet again at HP to get a sense of scale of the Web Press room so we can scale our prototype correctly.
There were not a whole lot of problems. The only real problems I foresee are that it is hard to get together and work on this project, and that I and the others in our group have a pretty full class load, so we aren’t spending as much time on this project as we would like.
We plan to meet next week to develop together, and to get a prototype level up and running so that we can show Tim at our next meeting.\\

\textbf{Feb 1, 2019}\\
This week was a productive one for us! We all got involved in development and started really getting into the swing of things. There is now a working prototype level with a rough training scenario, a menu UI system, and a model of the press currently being made. These are essential pieces, and it feels good to have made progress on them. We showed what we have now to our client today (Friday) and he liked what he saw.
No real problems came up this week. We set a goal for what we would have done this week and we actually finished all of that!
Next steps are going to be to polish the press room we have now. An important piece of VR is immersion and creating the sense of inhabiting a real space, and that is going to take some design work to fill out the level. We also want to make a training room that will teach first time users how to use VR. This is something our client clearly cares about, and would be a good way to teach users the basics of our application.\\

\textbf{Feb 8, 2019}\\
This week we made some pretty good progress. We got a main level up and running, so now our room is not just a sad little test map. Stephen modeled the web press and that is in the project now, and it looks great. I also did a lot of project cleaning (a game project file structure gets messy quick with a lot of people touching it).
There was only one small problem this week, and it’s that Stewart’s UI implementation was hard to merge with the main project. Something about his personal development environment wasn’t compatible with our project. That whole situation is still in progress.
We plan to keep polishing the main level and light scenario. Immersion is really important to us, so we want to spend a lot of time making sure the place feels real. We also want to implement a training room that will help introduce VR to new users.\\

\textbf{Feb 16, 2019}\\
This week we made good progress on the project. We have continued to polish the level, added more interactions, and integrated the menu UI system to the main project. There have also been improvements made to the web press model to make it more realistic.
There were no major problems this week, mostly just trying to get as much done as possible and checking things off the to do list.
Our plans for this next week are to try to complete a whole training scenario from start to finish, complete with UI. We also hope to start work on a tutorial room to teach users the basics of our app.\\

\textbf{Feb 21, 2019}\\
I’m doing this a day early because I will be out of town all day tomorrow (Friday). This week was a bit slower than other weeks, but a lot was still accomplished. I know personally I wasn’t able to get as much done on the project this week due to other classes, but the team as a whole made some good forward progress. We got the printer model updated, and also started implementing functionality for both the tutorial and the main training scenario (replacing an overheated print head).
We ran into a little problem merging different versions of the project. Stewart has been primarily handling UI and tutorial stuff, and the merge broke some references to updated assets. Nothing major, but a reminder of the dangers of working on different versions of the project.
This next week we will continue to work on the tutorial and main training scenario. We want to make sure that these work and can be tested from start to finish, even if they are not particularly polished yet.\\

\textbf{March 1, 2019}\\
This week was pretty good. We made progress on the tutorial section and it is essentially feature complete. It is a little buggy, but we are happy with the overall flow of the tutorial at this point. More progress was also made on the main training scenario. The interaction with the printer pieces was polished and all that needs to be done is to hook the printer state up to some UI elements.
Progress this week was good, and the only problems we had were just that a couple of our team got pretty sick this week. Luckily we were still able to achieve a lot of our goals for the week.
Plans include: hooking the main training scenario up to UI, polishing user interaction mechanics, and improvements to the 3D environment.\\

\textbf{March 11, 2019}\\
Sorry this is late!
This week some good progress was made on the project. We were able to get both the tutorial and main training scenario completed. They are not totally polished, but the scenario can be ran from start to finish. The warehouse environment also got lighting and material improvements, trying to make the space more readable and realistic.
Problems this week are just that I wish I had more time for the project, but other classes are destroying me! We also have a sick team member, but we have been able to keep up.
Our plans include polishing the tutorial and training scenario, more environment polish, and doing end of term documentation.\\

\textbf{March 15, 2019}\\
This week no huge steps were taken on the project, as we are all pretty much swamped because of finals stuff. We have mostly been talking about what all we need to ensure we are set for beta release, and the consensus is that we are basically there. All of the core elements are in place, they just need more polish which will come at the start of next term.
This week I had a version control problem. I had made some new materials and revamped the lighting, and for some reason my changes were lost. I think I wasn’t on the most recent version of the project, something just went wrong somewhere. Not a huge deal, just need to put in more time to redo that.
Our plans for this next week are to add some finishing touches to the project, finish our write up, and record the progress video on Monday.\\

\textbf{Apr 5, 2019}\\
This week we set up group meeting times, set a meeting with our client for next week, and set TA meeting times. We also talked over what is top priority for code freeze, and we decided to focus on integrating sound, writing a good user guide, and making sure that the full scenario can be completed easily when running the app as a standalone executable.
We plan to work on these things over the next couple weeks and then continue to polish the project for expo. I personally am interested in adding a couple touches to make the experience more fun to show off to users, because I see that people really like to play around in VR, and that’s the kind of stuff I like to make. We have really hit all of our requirements, so I want to take some time to implement things from our “wishlist”.\\

\textbf{Apr 12, 2019}\\
This week we got a lot done! There were some bugs related to controller inputs that had been plaguing us for a bit, but I found that it was just due to some incompatible plugins in Unreal. We also added sound, cleaned up the project file structure, added in more interactable objects, and added tooltips to the controllers.
We still need to put together instructions for the graders, and build and test an executable version of our project. Unreal is weird, so I’m hoping that is easy, but I really don’t know yet. The combo of Unreal, the SteamVR API, and the HP headset has kind of been a headache to develop for.\\

\textbf{Apr 19, 2019}\\
Not a lot happened this week besides preparing for code freeze. There were a few issues that came up when we were trying to build an executable from our project, but nothing that was too much to handle. That got all submitted in time, we verified some info for expo.
We are having a little trouble getting a hold of our client. He has been relatively unresponsive. He did reply a couple days ago and apologized for the slow reply and that he would look over the documentation soon. Besides this, everything is coming together! We are looking to polish up a couple things before expo, maybe add some fun interactions and objects for the live demo, but that’s about it.\\

\textbf{Apr 27, 2019}\\
This week not a whole lot happened. There are a few things we still might want to implement in the project, but nothing that really needs to go in before expo. We really just plan to go through it a few times to make sure there is nothing we need to streamline more for the live demo.
Something I want to do is make a level that doesn't have any event logic tied to it, so we can just have users look around and poke at the environment. It might be cool to put some more fun objects in to give them something interesting to mess around with. The live demo isn't strictly necessary, so I want to make sure it is enjoyable for users to mess with.
This week we also got together a final draft of the poster for review, and will send that off for printing as soon as it is okayed.\\

\textbf{May 3, 2019}\\
A little late on this one, sorry! Not a lot again happened this week. We finished up our poster, got model release forms turned in, and are mentally preparing for expo. Not a whole lot left to do, we are looking good!\\

\textbf{May 10, 2019}\\
Not a lot again this week. We went to class and got filled in on most everything we needed to know about expo. We are ready!!! There is a list of stuff we know we need, and have backup plans in case anything falls through. \\

